%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
	{University of California, Santa Barbara} % Organization
	{Networking Research Assistant} % Job title
	{Santa Barbara, CA, USA} % Location
	{Jan. 2021 - now} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Working under supervision of Prof. Arpit Gupta}
			\item {Researching applied Machine Learning in Networking, including XAI, reproducibility, and network data representation.}
			\item {Working on pipeline-based solution for networking active measurement experiments.}
		\end{cvitems}
	}
	
%---------------------------------------------------------
\cventry
	{Huawei} % Organization
	{On-Device Machine Learning Researcher} % Job title
	{St. Petersburg, Russia} % Location
	{Mar. 2020 - Sep. 2021} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Researching onboard Machine Learning techniques, network distillation, pruning, mobile device inference.}
			\item {Designing ML-based system for Android devices.}
			\item {Designed and implemented a custom Forward Error Correction algorithm for Huawei mobile devices.}
			\item {Designed and prototyped a system for user network performance using both on-device and operator information.}
		\end{cvitems}
	}
	
%---------------------------------------------------------
  \cventry
	{JetBrains Research} % Organization
	{Research intern} % Job title
	{St. Petersburg, Russia} % Location
	{Oct. 2019 - Jun. 2020} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Reproduced several articles in order to confirm achieved results.}
			\item {Implemented a novel World Models-based approach for Prioritized Experience Replay}
			\item {Prepared and held several talks about current progress in Reinforcement Learning field}
		\end{cvitems}
}

%---------------------------------------------------------
  \cventry
    {Higher School of Engineering} % Organization
    {Python tutor} % Job title
    {St. Petersburg, Russia} % Location
    {Sep. 2018 - Oct. 2020} % Date(s)
    {
		\begin{cvitems} % Description(s) of tasks/responsibilities
		 \item {Designed several Python courses for different kinds of listeners.}
		 \item {Semi-automated home task checking with unit tests and GitHub.}
		 \item {Wrote a task book for Python learners with tasks ordered by complexity.}
		 \item {Recorded video lectures and prepared courses for online education.}
		\end{cvitems}
    }

%---------------------------------------------------------
  \cventry
	{Higher School of Engineering} % Organization
	{System administrator} % Job title
	{St. Petersburg, Russia} % Location
	{Jul. 2015 - Jun. 2019} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Implemented failover solution for the data storage network.}
			\item {Expanded and augment existing virtual machines infrastructure.}
			\item {Deployed advanced network and infrastructure monitoring services (like IDS, IPAM, centralized logging, etc.).}
			\item {Expanded domain and infrastructure to several branch offices.}
			\item {Created solution for HTML5-based access to virtual machines on Hyper-V/SCVMM hosts.}
		\end{cvitems}
	}

%---------------------------------------------------------
\end{cventries}
