%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Open-source contributions}

\begin{cvopensource}
	\cvopensourceentry{digestbot}{
		https://github.com/artyomche9/digestbot/commits?author=maybe-hello-world
	}{ODS.AI}{
		\begin{itemize}
			\item Project: slack bot for finding hot topics and important messages.
			\item Main maintainer and architector of the project.
			\item Contribution: architecture, crawler code, UI code, internal logic, deploy and maintaining.
		\end{itemize}
	}%
%
	\cvopensourceentry{Tortilla}{}{maybe-hello-world}{
	\begin{itemize}
		\item Project: HTML5 web interface for Hyper-V virtual machine with role-based access (based on Apache Guacamole).
		\item Main maintainer and architector of the project.
		\item Contribution: architecture, UI, backend (except Java wrapper for Guacamole), deploy.
	\end{itemize}
	}%
%
	\cvopensourcesmallentry{PowerShell}{
		https://github.com/PowerShell/PowerShell/commits?author=maybe-hello-world
	}{Microsoft}{
		Proposed and added additional arguments to commands for working with PFX certificates.
	}%
	\cvopensourcesmallentry{Posh-ACME}{
	https://github.com/rmbolger/Posh-ACME/commits?author=maybe-hello-world%
	}{rmbolger}{
		Fixed incorrect error ignoring, which prevented automation of several tasks.
	}
	\cvopensourcesmallentry{xcp-lab-cli}{
		https://github.com/spbstu/xcp-lab-cli/commits/master?author=maybe-hello-world%
	}{SPbSTU}{
		Bugfixes, implemented cleanup of old labs, teacher VM creation and other functions.
	}
%
\end{cvopensource}